Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over convex domains and domains with shellable triangulations

### 2024-09-29 main.tex
section on gradient potentials over triangulated domains

\documentclass[10pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\input{header}

@@

\title{Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over \cye{convex domains and} domains with shellable triangulations}
\author{
    Th\'eophile Chaumont-Frelet\thanks{Affiliation of the First Author, \texttt{email1@example.com}} \and
    Martin Werner Licht\thanks{Affiliation of the Second Author, \texttt{martin.licht@epfl.ch}} \and
    Martin Vohral\'ik\thanks{\cye{Inria, 48 rue Barrault, 75647 Paris, France \& CERMICS, Ecole des Ponts, 77455 Marne-la-Vall\'ee, France}, \texttt{\cye{martin.vohralik@inria.fr}}}
}

@@

\tableofcontents
\todo[inline]{MV: Added table of contents: for us, to see the structure of and the main terminology used in the paper}

@@

We introduce a specific notion of connectivity. 
Given an $n$-dimensional simplicial complex $\calT$, 
we call $n$-simplices $S,S' \in \calT$ \emph{face-connected in $\calT$} if there exists a sequence $S_0=S,S_1,\dots,S'=S_m \in \calT$ such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$. % TODO: Theo suggests reverse order of that sequence 
We call such a sequence a \emph{strong path} from $S$ to $S'$ in $\calT$. 
Clearly, face-connected in $\calT$ is an equivalence relation among simplices. 
A \emph{face-connected component} of $\calT$ is an equivalence class under this equivalence relation, 
and we call $\calT$ \emph{face-connected} if it has only one face-connected component. 
\\

@@

We are interested in the maximal ratio of volumes between \mwl{face?} neighboring $n$-simplices, written $\volumeratio(\calT)$,
and the ratio of intersecting simplices, written $\diameterratio(\calT)$. Formally, 
\begin{align}
    \volumeratio(\calT) 
    := 
    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } 
    \frac{ \vol(T) }{ \vol(T') }
    ,
    \qquad 
    \diameterratio(\calT) 
    := 
    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \neq \emptyset } }
    \frac{ \diam(T) }{ \diam(T') }
    .
\end{align}
Finally, whenever $T, T'$ are two $n$-simplices that share a common face $F$ of codimension $1$, we let $\Xi_{T,T'} : T \rightarrow T'$ denote the affine diffeomorphism 
that preserves $F$. We then define 
\begin{align}\label{math:reflectionmeasure}
    \reflectionestimate(\calT) 
    := 
    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } }
    \matnorm{ \Jacobian \Xi_{T,T'} }
\end{align}
to be the maximum of the operator norm of the Jacobian of any such diffeomorphism. 
This indicator quantifies how much reflection across the shared face distorts the geometry.

@@

\begin{remark}
    Lemma~\ref{lemma:volumecomparison} fully controls the shape quantity $\rho(\calT)$ \cye{of~\eqref{math:volumecomparisonmeasure}} but not $\theta(\calT)$ \cye{of~\eqref{math:diametercomparison}}. 
    Lemma~\ref{lemma:volumecomparison} fully controls the shape quantity $\volumeratio(\calT)$ but not $\diameterratio(\calT)$. 
    As seen above, we can bound the ratio of diameters and volumes of simplices that share at least one face in terms of the shape measure. 
    If we have an upper estimate for the number of simplices sharing a given vertex, 
    we can also bound the ratios of diameters and volumes of simplices sharing only a single common vertex. 
\end{remark}
%%%%%%%% END HERE

@@

In this section we address the stepwise computable estimate of Poincar\'e--Friedrichs constants of triangulated domains. 
We achieve by explicitly constructing scalar potentials of gradients.
We have already seen that we can construct the scalar potential for a gradient vector field by a well-understood procedure if the domain is convex: after fixing a starting point, we integrate the gradient vector field along lines emanating from that starting point. We take that procedure as in inspiration for constructing gradient potentials over more general triangulated domains: after fixing a starting cell, we construct the potential by successive integration over more and more cells. we construct a scalar potential for a given gradient vector field on larger and larger simplicial neighborhoods. 
The basic idea has appeared in the different variants before, for instance recently in \cite{Ern_Voh_p_rob_3D_20, Chaum_Voh_p_rob_3D_H_curl_23, Voh_loc_glob_H1_24}.
\\

{\color{blue}In this section\cye{,} we \cye{develop a} stepwise computable estimate of Poincar\'e--Friedrichs constants of triangulated domains. \cye{The following very classical procedure serves us as an inspiration:} given a gradient vector field, we can reconstruct \cye{the scalar potential} up to a constant by fixing a starting point and integrating the gradient vector field along lines emanating from that starting point. 
Over triangulated domains, \cye{we fix} a starting triangle \cye{and perform this classical procedure. We then pass through the triangulation such that each subsequent simplex is connected to the previous ones by a face}. 
We always construct a gradient potential over the new simplex and fix the constant using the value already known on the connecting face.
This basic idea has appeared in the different variants before, for instance recently in \cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24, Voh_loc_glob_H1_24}.
}

We construct scalar potentials over larger and larger intermediate subdomains. 
Two different variations of that idea are analyzed;
while the underlying idea remains the same, they differ in the way the intermdiate potentials are extended.
On the one hand, we can cover the domain with overlapping simplicial patches (such as face patches), over which local scalar potentials are easily found. Since these can only differ by constants at their overlaps, we can assemble a global scalar potential piece by piece. This is described in Theorem~\ref{theorem:poincarefriedrichsestimate:grad} and relies on Lemma~\ref{lemma:poincarefriedrichsoverfacepatch} as an auxiliary result.

For the agenda of this section, the following combinatorial notion of triangulations will be helpful. 
Whenever $\calT$ is a face-connected $n$-dimensional triangulation, 
a \emph{spanning tree} is an enumeration $T_{0}, \dots, T_{M}$ of all its $n$-dimensional simplices
where for each index $1 \leq m \leq M$ we have fixed index $0 \leq j(m) \leq m-1$ 
such that $T_{m}$ and $T_{j(m)}$ share a common face of dimension $n-1$.
We call $T_{j(m)}$ the \emph{predecessor} of $T_{m}$ within the spanning tree.

On the other hand, we assess an alternative route towards constructing scalar gradient potentials over triangulated domains. 
While the underlying idea remains the same, the construction of the potential is slightly different. 
we can extend the potential on each intermediate domain to another simplex by solving a local auxiliary problem on that simplex subject to partial boundary conditions. This is described in Theorem~\ref{theorem:poincarefriedrichsestimate:gradzwei}. 
As an auxiliary result with independent relevance, Lemma~\ref{lemma:mixedbconsimplex} computes an upper bound for the Poincar\'e--Friedrichs inequality when homogeneous boundary conditions are imposed on a single face of the boundary.

We emphasize that the second approach to constructing potentials and bounding Poincar\'e--Friedrichs constants serves as the blueprint for constructing potentials of the curl and divergence operators in later sections. Our estimates of Poincar\'e--Friedrichs constants capture the correct asymptotic behavior as $p$ grows to infinity.

{\color{blue}\cye{We start by extending the results on Poincar\'e--Friedrichs constants over convex domains from Section~\ref{section: PX_convex} to face patches within simplicial triangulations} in a way which captures the correct asymptotic behavior as $p$ grows to infinity. \cye{Let us stress that face patches are not necessarily convex and remark that our result is in particular sharp when $T_1$ and $T_2$ have similar volumes and diameters}.}

\begin{lemma}\label{lemma:poincarefriedrichsoverfacepatch}
    Let $\calT$ be a triangulation.
    Let $T_{1}, T_{2} \in \calT$ be two $n$-simplices whose intersection is a common facet $F := T_1 \cap T_2$. 
    Write $U := T_1 \cup T_2$. 
    Then 
    \begin{align*}
        \min\limits_{ c \in \bbR }
        \| u - c \|_{L^{p}(U)}
        &
%         \leq 
%         2 \Ceins{n} C_{\PF,{\rm EFNT},p}
%         \max\left( 
%             \frac{ \vol(T_1) }{ \vol(T_2) }
%             ,
%             \frac{ \vol(T_2) }{ \vol(T_1) }
%         \right)^{\frac 1 p}
%         \\&\qquad\qquad 
%         \cdot 
%         \max\left( \diam(T_1), \diam(T_2) \right)
%         \| \nabla u \|_{L^{p}(U)}
%         \\&
        \leq 
        2 \Ceins{n} C_{\PF,{\rm EFNT},p}
        \volumeratio(\calT)^{\frac 1 p}
        \max\left( \diam(T_1), \diam(T_2) \right)
        \| \nabla u \|_{L^{p}(U)}
    \end{align*}
    for any $u \in W^{1,p}(\Omega)$ with $p \in [1,\infty]$. \mwl{Introduce constant $C_{{\rm{PF}},T_1 \cup T_2,p}$}
\end{lemma}
% \begin{remark}
%     The result is sharp when $T_1$ and $T_2$ have equal volume and diameter, and that $U$ is not necessarily convex. 
% \end{remark}
\begin{proof}
    Without loss of generality, $F$ has the vertices $v_0, \dots, v_{n-1}$,
    and $z_{1} \in T_{1}$ and $z_{2} \in T_{2}$ are the remaining vertices of the two triangles. 
    Let $\Delta_{1} = \Delta^{n}$ be the reference $n$-simplex and let $\Delta_{2}$ be obtained from it by flipping the $n$-th coordinate.
    We let $\varphi_{1} : \Delta_{1} \rightarrow T_{1}$ and $\varphi_{2} : \Delta_{2} \rightarrow T_{2}$
    be affine transformations that map the $e_{i}$ to $v_{i}$ for $i = 0, \dots, n-1$ 
    and which satisfy $\varphi_{1}(e_{n}) = z_{1}$ and $\varphi_{2}(-e_{n}) = z_{2}$.
    Write $\hat U := \Delta_1 \cup \Delta_2$, which is (crucially) convex. .
    We have a bi-Lipschitz mapping $\varphi : \hat U \rightarrow U$.

@@

    Notice that $\hat U$ is convex and has diameter $2$. 
    Thus, due to~\eqref{math:esposito:pf}, there exists $\hat w \in W^{1,p}(\hat U)$ such that $\nabla \hat w = \nabla \hat u$ and 

@@

    \cye{In the last equality, we have also used $|\det(\Jacobian\varphi_i)| = n! \vol(T_i)$ that we have already employed in~\eqref{equation:Hong_Pan}.}
    Noting $\vol(T_i) = |\det(\Jacobian \varphi_i)|$ and $\matnorm{ \Jacobian \varphi_i } \leq \Ceins{n} \diam(T_i)$ for $i = 1, 2$, where we use Lemma~\ref{lemma:measurerelationships}, we conclude the desired result.

@@

\begin{figure}[t]
\begin{center}
\begin{tikzpicture}
    \coordinate (A) at (0,0);
    \coordinate (B) at (2,0);
    \coordinate (C) at (1,1.5);
    \coordinate (D) at (3,1.5); 
    \coordinate (E) at (3,3); 
    \coordinate (F) at (4,0.25); 
    \coordinate (X) at (1,-1.5);
    \coordinate (Y) at (3,-1.5); 
    \coordinate (T) at (5,2);

@@

%     \node at (A) [below left] {$A$};
%     \node at (B) [below right] {$B$};
%     \node at (C) [above] {$C$};
%     \node at (D) [above right] {$D$};
%     \node at (T) [above right] {$T$};
\end{tikzpicture}
\end{center}
\caption{Strongly connected triangulation of a domain. The arrows depict a tree in the strong connection graph of the form used in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}. The triangle in dark gray is the triangle being added in the current iteration, and the light gray triangles constitute the subdomain assembled so far.}
\end{figure}

\begin{figure}[t]
\begin{center}
\begin{tikzpicture}
    \coordinate (A) at (0,0);   \coordinate (B) at (2,0); \coordinate (C) at (1,1.5);
    \coordinate (D) at (0,2.9); \coordinate (E) at (2.5,3); \coordinate (F) at (3,1.25); 
    \draw[fill=gray!50] (A) -- (B) -- (C) -- cycle; 
    \draw[fill=white  ] (A) -- (C) -- (D) -- cycle; 
    \draw[fill=white  ] (C) -- (D) -- (E) -- cycle; 
    \draw[fill=white  ] (B) -- (C) -- (F) -- cycle; 
\end{tikzpicture}
\quad
\begin{tikzpicture}
    \coordinate (A) at (0,0);   \coordinate (B) at (2,0); \coordinate (C) at (1,1.5);
    \coordinate (D) at (0,2.9); \coordinate (E) at (2.5,3); \coordinate (F) at (3,1.25); 
    \draw[fill=gray!25] (A) -- (B) -- (C) -- cycle; 
    \draw[fill=gray!50] (A) -- (C) -- (D) -- cycle; 
    \draw[fill=white  ] (C) -- (D) -- (E) -- cycle; 
    \draw[fill=white  ] (B) -- (C) -- (F) -- cycle; 
\end{tikzpicture}
\quad
\begin{tikzpicture}
    \coordinate (A) at (0,0);   \coordinate (B) at (2,0); \coordinate (C) at (1,1.5);
    \coordinate (D) at (0,2.9); \coordinate (E) at (2.5,3); \coordinate (F) at (3,1.25); 
    \draw[fill=gray!25] (A) -- (B) -- (C) -- cycle; 
    \draw[fill=gray!25] (A) -- (C) -- (D) -- cycle; 
    \draw[fill=gray!50] (C) -- (D) -- (E) -- cycle; 
    \draw[fill=white  ] (B) -- (C) -- (F) -- cycle; 
\end{tikzpicture}
\quad
\begin{tikzpicture}
    \coordinate (A) at (0,0);   \coordinate (B) at (2,0); \coordinate (C) at (1,1.5);
    \coordinate (D) at (0,2.9); \coordinate (E) at (2.5,3); \coordinate (F) at (3,1.25); 
    \draw[fill=gray!25] (A) -- (B) -- (C) -- cycle; 
    \draw[fill=gray!25] (A) -- (C) -- (D) -- cycle; 
    \draw[fill=gray!25] (C) -- (D) -- (E) -- cycle; 
    \draw[fill=gray!50] (B) -- (C) -- (F) -- cycle; 
\end{tikzpicture}
\end{center}
\caption{Exhausting a domain step by step as in Theorem~\ref{theorem:poincarefriedrichsestimate:grad} and \ref{theorem:poincarefriedrichsestimate:gradzwei}.
The dark gray triangle is the one being currently added, and the light gray triangles constitute the subdomain assembled so far.}
\label{figure:exhausting}
\end{figure}

>>>>

\documentclass[10pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
%\usepackage[margin=0.1cm]{geometry}
\input{header}

@@

\title{Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over convex domains and domains with shellable triangulations}
\author{
    Th\'eophile Chaumont-Frelet\thanks{Affiliation of the First Author, \texttt{email1@example.com}} \and
    Martin Werner Licht\thanks{Affiliation of the Second Author, \texttt{martin.licht@epfl.ch}} \and
    Martin Vohral\'ik\thanks{\cye{Inria, 48 rue Barrault, 75647 Paris, France \& CERMICS, Ecole des Ponts, 77455 Marne-la-Vall\'ee, France}, \texttt{\cye{martin.vohralik@inria.fr}}}
}

@@

\tableofcontents

@@

We introduce a specific notion of connectivity when we are given an $n$-dimensional simplicial complex $\calT$. 
We call two $n$-dimensional simplices $S, S' \in \calT$ \emph{face-neighboring} if $S \cap S'$ is a common face of both of them. 
We call $n$-simplices $S,S' \in \calT$ \emph{face-connected in $\calT$} if there exists a sequence $S_0=S,S_1,\dots,S'=S_m \in \calT$ such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$. % TODO: Theo suggests reverse order of that sequence 
We call such a sequence a \emph{strong path} from $S$ to $S'$ in $\calT$. \mwl{Change the terminology strong path to something else.}
Clearly, face-connected in $\calT$ is an equivalence relation among simplices. 
A \emph{face-connected component} of $\calT$ is an equivalence class under this equivalence relation, 
and we call $\calT$ \emph{face-connected} if it has only one face-connected component.

\mwl{We should use clarify face vs facet}

\subsection{...}

@@

We are interested in the maximal ratio of volumes between \mwl{face?} neighboring $n$-simplices, written $\volumeratio(\calT)$,
and the ratio of intersecting simplices, written $\diameterratio(\calT)$. Formally, 
\begin{align}\label{math:volumeratio}
    \volumeratio(\calT) 
    := 
    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } 
    \frac{ \vol(T) }{ \vol(T') }
    ,
\end{align}
\begin{align}\label{math:diameterratio}
    \diameterratio(\calT) 
    := 
    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \neq \emptyset } }
    \frac{ \diam(T) }{ \diam(T') }
    .
\end{align}
Finally, whenever $T, T'$ are two $n$-simplices that share a common face $F$ of codimension $1$, we let $\Xi_{T,T'} : T \rightarrow T'$ denote the affine diffeomorphism 
that preserves $F$. We then define 
\begin{align}\label{math:reflectionmeasure}
    \reflectionestimate(\calT) 
    := 
    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } }
    \matnorm{ \Jacobian \Xi_{T,T'} }
\end{align}
to be the maximum of the operator norm of the Jacobian of any such diffeomorphism. 
This indicator quantifies how much reflection across the shared face distorts the geometry.

@@

\begin{remark}
    Lemma~\ref{lemma:volumecomparison} fully controls the shape quantity $\volumeratio(\calT)$ \cye{of~\eqref{math:volumeratio}} but not $\diameterratio(\calT)$ \cye{of~\eqref{math:diametercomparison}}. 
    Lemma~\ref{lemma:volumecomparison} fully controls the shape quantity $\volumeratio(\calT)$ but not $\diameterratio(\calT)$. 
    As seen above, we can bound the ratio of diameters and volumes of simplices that share at least one face in terms of the shape measure. 
    If we have an upper estimate for the number of simplices sharing a given vertex, 
    we can also bound the ratios of diameters and volumes of simplices sharing only a single common vertex. 
\end{remark}
%%%%%%%% END HERE

@@

\mwl{In this section, we develop a stepwise computable estimate of Poincar\'e--Friedrichs constants of triangulated domains. 
The following very classical procedure serves us as an inspiration: given a gradient vector field, we can reconstruct the scalar potential up to a constant by fixing a starting point and integrating the gradient vector field along lines emanating from that starting point. 
We perform a discrete analogue of this procedure over triangulated domains: 
having fixed a starting triangle, we traverse the triangulation along face-neighboring simplices.
%We construct a scalar potential for a given gradient vector field on larger and larger triangulated subdomains.
We always construct a gradient potential over the new simplex and fix the constant using the value already known on the connecting face, thus constructing a scalar potential over larger and larger subdomains.
This basic idea has appeared in the different variants before, for instance recently in \cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24, Voh_loc_glob_H1_24}.}

% We have already seen that we can construct the scalar potential for a gradient vector field by a well-understood procedure if the domain is convex: after fixing a starting point, we integrate the gradient vector field along lines emanating from that starting point. We take that procedure as in inspiration for constructing gradient potentials over more general triangulated domains: after fixing a starting cell, we construct the potential by successive integration over more and more cells. We construct a scalar potential for a given gradient vector field on larger and larger simplicial neighborhoods. 
% This basic idea has appeared in the different variants before, for instance recently in \cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24, Voh_loc_glob_H1_24}.
% 
% {\color{blue}In this section\cye{,} we \cye{develop a} stepwise computable estimate of Poincar\'e--Friedrichs constants of triangulated domains. \cye{The following very classical procedure serves us as an inspiration:} given a gradient vector field, we can reconstruct \cye{the scalar potential} up to a constant by fixing a starting point and integrating the gradient vector field along lines emanating from that starting point. 
% Over triangulated domains, \cye{we fix} a starting triangle \cye{and perform this classical procedure. We then pass through the triangulation such that each subsequent simplex is connected to the previous ones by a face}. 
% We always construct a gradient potential over the new simplex and fix the constant using the value already known on the connecting face.
% This basic idea has appeared in the different variants before, for instance recently in \cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24, Voh_loc_glob_H1_24}.
% }

% While the underlying idea remains the same, they differ in the way the intermdiate potentials are extended.
% This is described in Theorem~\ref{theorem:poincarefriedrichsestimate:grad} and relies on Lemma~\ref{lemma:poincarefriedrichsoverfacepatch} as an auxiliary result. 
% This is described in Theorem~\ref{theorem:poincarefriedrichsestimate:gradzwei}.

We begin with an auxiliary result with independent relevance, where we estimate the Poincar\'e--Friedrichs inequality when homogeneous boundary conditions are imposed along a single face of the boundary. 
% This is inspired by the classical proof of what is often called Friedrichs' inequality.
    If $u \in W^{1,p}(T)$ with $\trace_{F} u = 0$, then 
    where $C_{\PF,T,F,p} = p^{-\frac 1 p} \diam(T)$ for $p < \infty$ and $C_{\PF,T,F,\infty} = \diam(T)$. 
    We extend $u$ by zero to a function over the entire $\bbR^{n}$.
    the segment from the midpoint of $F$ to the opposing vertex lies on the first coordinate axis,
    We write $\bfg$ for the trivial extension of $\nabla u$ over the entire $\bbR^{n}$.
    There exists affine diffeomorphism $\varphi : \Delta^{n} \rightarrow T$ from the reference simplex onto $T$ that maps the convex closure of the $n$ unit vectors onto the face $F$.
    Now $u_{m} \circ \varphi^{-1} \in C^{\infty}(\hat U)$ approximates $u$ within the Banach space $W^{1,p}(T)$
    and has the desired support property. 

The next auxiliary result extends the results on Poincar\'e--Friedrichs constants over convex domains from Section~\ref{section: PX_convex} to face patches within simplicial triangulations. We point out that face patches are not necessarily convex. The following result is reasonably sharp when the two simplices have similar volumes and diameters.

\begin{lemma}\label{lemma:poincarefriedrichsoverfacepatch}
    Let $\calT$ be a triangulation.
    Let $T_{1}, T_{2} \in \calT$ be two $n$-simplices whose intersection is a common facet $F := T_1 \cap T_2$. 
    Write $U := T_1 \cup T_2$. 
    If $p \in [1,\infty]$ and $u \in W^{1,p}(\Omega)$,
    then 
    \begin{align*}
        \min\limits_{ c \in \bbR }
        \| u - c \|_{L^{p}(U)}
        &
%         \leq 
%         2 \Ceins{n} C_{\PF,{\rm EFNT},p}
%         \max\left( 
%             \frac{ \vol(T_1) }{ \vol(T_2) }
%             ,
%             \frac{ \vol(T_2) }{ \vol(T_1) }
%         \right)^{\frac 1 p}
%         \\&\qquad\qquad 
%         \cdot 
%         \max\left( \diam(T_1), \diam(T_2) \right)
%         \| \nabla u \|_{L^{p}(U)}
%         \\&
        \leq 
        C_{{\rm{PF}},T_1 \cup T_2,p}
        \| \nabla u \|_{L^{p}(U)}
        .
    \end{align*}
    Here, $C_{{\rm{PF}},T_1 \cup T_2,p} = 2 \Ceins{n} C_{\PF,{\rm EFNT},p} \volumeratio(\calT)^{\frac 1 p} \max\left( \diam(T_1), \diam(T_2) \right)$. 
\end{lemma}
% \begin{remark}
%     The result is sharp when $T_1$ and $T_2$ have equal volume and diameter, and that $U$ is not necessarily convex. 
% \end{remark}
\begin{proof}
    Without loss of generality, $F$ has the vertices $v_0, \dots, v_{n-1}$,
    and $z_{1} \in T_{1}$ and $z_{2} \in T_{2}$ are the remaining vertices of the two triangles. 
    Let $\Delta_{1} = \Delta^{n}$ be the reference $n$-simplex and let $\Delta_{2}$ be obtained from it by flipping the $n$-th coordinate.
    We let $\varphi_{1} : \Delta_{1} \rightarrow T_{1}$ and $\varphi_{2} : \Delta_{2} \rightarrow T_{2}$
    be affine transformations that the origin to $v_0$, that map each unit vector $e_{i}$ to $v_{i}$ for $i = 1, \dots, n-1$,
    and that satisfy $\varphi_{1}(e_{n}) = z_{1}$ and $\varphi_{2}(-e_{n}) = z_{2}$.
    Write $\hat U := \Delta_1 \cup \Delta_2$.
    We have a bi-Lipschitz mapping $\varphi : \hat U \rightarrow U$.

@@

    Notice that $\hat U$ has diameter $2$ and is (crucially) convex. 
    Thus, due to Poincar\'e--Friedrichs inequality~\eqref{math:esposito:pf}, there exists $\hat w \in W^{1,p}(\hat U)$ such that $\nabla \hat w = \nabla \hat u$ and 

@@

    For both $i = 1,2$, we now recall the well-known equation $|\det(\Jacobian\varphi_i)| = n! \vol(T_i)$, 
    % which we have already employed in~\eqref{equation:Hong_Pan}, 
    and the estimate $\matnorm{ \Jacobian \varphi_i } \leq \Ceins{n} \diam(T_i)$, which is given in Lemma~\ref{lemma:measurerelationships}. We conclude the desired result.

@@

The main result of this section constructs a potential and gives an upper bound for the Poincar\'e--Friedrichs constant.  
It has the same building principle as the ``discrete mean Poincar\'e inequality'' of~\cite[Lemma~3.7]{Eym_Gal_Her_00}.
The procedure serves as the blueprint for constructing potentials of the curl and divergence operators in later sections.

Two different variations of underlying idea are analyzed. 
On the one hand, we extend the scalar gradient potentials over each intermediate domain to another simplex by solving a local auxiliary problem on that simplex. This auxiliary problem will be subject to partial boundary conditions. 
% We present an auxiliary result with independent relevance, Lemma~\ref{lemma:mixedbconsimplex}, where we compute an upper bound for the Poincar\'e--Friedrichs inequality when homogeneous boundary conditions are imposed along a single face of the boundary. 
% We emphasize that this construction of potentials and bounding of Poincar\'e--Friedrichs constants serves as the blueprint for constructing potentials of the curl and divergence operators in later sections. 
On the other hand, we can instead cover the domain with overlapping simplicial patches (such as face patches), over which local scalar potentials are easily found. Since these can only differ by constants at their overlaps, we can assemble a global scalar potential piece by piece by adjusting the local constants of integration. 
Both estimates of Poincar\'e--Friedrichs constants capture the correct asymptotic behavior as $p$ grows to infinity.

For the remainder of this section, the following combinatorial notion of triangulations is used. 
Whenever $\calT$ is a face-connected $n$-dimensional triangulation, 
a \emph{spanning tree} is an enumeration $T_{0}, \dots, T_{M}$ of all its $n$-dimensional simplices
where for each index $1 \leq m \leq M$ we have a fixed index $0 \leq \iota(m) \leq m-1$ 
such that $T_{m}$ and $T_{\iota(m)}$ are face-neighboring.
We call $T_{\iota(m)}$ the \emph{precursor} of $T_{m}$ within the spanning tree. 
The reader is referred to Figure~\ref{figure:spanningtree} for an illustration.

\begin{figure}[t]
\begin{center}
\begin{tikzpicture}[rotate=-60]
    \coordinate (A) at (0,0);
    \coordinate (B) at (2,0);
    \coordinate (C) at (1,1.5);
    \coordinate (D) at (3,1.5); 
    \coordinate (E) at (3,3); 
    \coordinate (F) at (4,0.25); 
    \coordinate (X) at (1,-1.5);
    \coordinate (Y) at (3,-1.5); 
    \coordinate (T) at (5,2);

@@

%     \node at (A) [below left] {$A$};
%     \node at (B) [below right] {$B$};
%     \node at (C) [above] {$C$};
%     \node at (D) [above right] {$D$};
%     \node at (T) [above right] {$T$};
\end{tikzpicture}
\end{center}
\caption{Face-connected triangulation of a domain. The arrows depict a spanning tree in the face-connection graph.}
\label{figure:spanningtree}
\end{figure}

\begin{theorem}\label{theorem:poincarefriedrichsestimate:grad}
    Let $\calT$ be a face-connected $n$-dimensional finite triangulation 
    with a spanning tree $T_0, T_1, \dots, T_{M}$. \mwl{should be a sequence with precursor function}
    For any $1 \leq m \leq \cye{M}$, let $F_m = T_m \cap T_{\iota(m)}$.
    Suppose $1 \leq p,q \leq \infty$ with $1 = 1/p + 1/q$,
    and that the domain $\Omega$ is the interior of the underlying set of $\calT$. 
    Then for any $u \in W^{1,p}(\Omega)$ 
    there exists $w \in W^{1,p}(\Omega)$ with $\nabla w = \nabla u$ 
    and such that for all $1 \leq m \leq M$
    we have the following recursive estimates:
    \begin{gather*}
        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\rm{PF}},T_{0},p} \| \nabla u \|_{L^{p}(T_{0})}.
    \end{gather*}
    and for $1 \leq m \leq M$ we have 
    \begin{align*}
        \| w \|_{L^{p}(T_{m})}
        &
        \leq  
        \volumeratio(\calT)^{\frac 1 p} 
        \| w \|_{L^{p}(T_{\iota(m)})} 
        + 
%         C_{\PF,T_{m},F_{m},p} 
%         \left( 
%             \| \nabla u \|_{L^{p}(T_{m})} 
%             + 
%             \volumeratio(\calT)^{\frac 1 p} \xi(\calT)
%             \| \nabla u \|_{L^{p}(T_{\iota(m)})}
%         \right)
        \left( 1 + \volumeratio(\calT)^{\frac q p} \xi(\calT)^{q} \right)^{\frac 1 q}
        C_{\PF,T_{m},F_{m},p} 
        \| \nabla u \|_{L^{p}(U_{F_m})} 
        ,
        \\
        \| w \|_{L^{p}(T_m)}
        &\leq 
        \volumeratio(\calT)^{\frac 1 p} 
        \| w \|_{L^{p}(T_{{\iota(m)}})}
        +
        \left( 1 + \volumeratio(\calT)^{\frac q p} \right)^{\frac 1 q}
        C_{{\rm{PF}},U_{F_m},p} 
        \| \nabla u \|_{L^{p}(U_{F_m})} 
        . 
    \end{align*}
\end{theorem}

\begin{proof}
    Let $u \in W^{1,p}(\Omega)$. 
    We start with the Poincar\'e--Friedrichs inequality on the first simplex $T_{0}$. 
    There exists $w_0 \in W^{1,p}(T_{0})$ satisfying $\nabla w_0 = \nabla u$ over $T_{0}$ together with 
    \begin{gather*}
    \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\rm{PF}},T_{0},p} \| \nabla u \|_{L^{p}(T_{0})}.
    \end{gather*}
    In particular, $c_{0} := w_0 - u$ is a constant function. 
    We then define 
    \begin{align*}
        w := u + c_0
        .
    \end{align*} 
    Clearly, $w \in W^{1,p}(\Omega)$ with $\nabla w = \nabla u$.
    By construction $w_{|T_{0}} = w_0$. 
    We verify that $w$ satisfies the two desired recursive estimates.
